---
title: "Developing Data Products Course Project"
author: "Nevon Donawa"
date: "December 26, 2018"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Concept
The purpose of this project was to develop, a tool to measure GDP growth frequency.
This web app produces a reactive histogram which illustrates a distribution of countries counted by their respective year over year gdp growth, based on the selected year.

##Data set
```{r}
gdproj9 <- read.csv("gdp.csv")
gdproj9 <- as.data.frame(gdproj9)
colnames(gdproj9)[3:14] <- c("2006", "2007", "2008", "2009", "2010", "2011", "2012", "2013", "2014", "2015", "2016", "2017")

head(gdproj9)
```

## Directions

1. Choose a year for GDP growth. 
2.Select the amount of bins for the frequency of countries by % of year over year gdp growth. 
3.The histogram will update to show how many countries, produced GDP at different levels.

The full application can be accessed here: https://ndonawa.shinyapps.io/GDPGrowth/


## Sample Output
Rather than plotting multiple histograms, the web app streamlines seeing trends yoy by selecting the a particular year and updating automatically..
```{r}
par(mfrow = c(2,1))
k17 <- hist(gdproj9$`2017`, main = "Frequency of Country GDP Growth in 2017", xlab = "Count of Country", col = "black")
k16 <- hist(gdproj9$`2016`, main = "Frequency of Country GDP Growth in 2016", xlab = "Count of Country", col = "grey")
```

